\mythesistitleNOTSYNPOSIS \tnote[fyi]{Synopsis title is ``Generalization of Consecutive Ones Property of Binary Matrices''}

### 2012-02-02 src/040chap4.tex
- a whole bunch of cleanups. see diff. - removed problem defs from chap 1. they were duplicates from chap 3. - CODED FIGURES IN TIKZ. forbidden subgraphs, graphmatrix example graphs. - BEGAN CHAPTER 3 EDITS.
Formatting/layout changes
-------

- Added FrenchLayout to make lists denser
- Added hanging indent for Definitions
- Compressed theorem env's above below spaces
- Creaded env for problem definition minipages.
- moved all clearpage/page counter and other prechapter settings to the chapter tex files.
- Fixed the page number bug in draft printout. removed \fancyhf{} to avoid resetting page n

@@

>>>>

There are optimization problems for matrices that do not have \COP
which we only mention here but do not discuss further in this
thesis. The central questions in this area are (i) how close is the
matrix to having \COP, mainly in terms of Tucker's forbidden
submatrices, and (ii) how optimally can one alter the matrix to attain
\COP.  With regard to the latter question, recent literature indicate
that there has been a lot of interest in matrix modification problems
to make a matrix have \COP \cite{hg02, tz07}. However, to tackle this
problem it is more than insightful to solve question (i).

To study the smallest hamming distance \temptext{(?)} between the
input matrix and one with \COP, identifying the Tucker's forbidden
substructures (See Section~\ref{sec:tucker} for detailed
  discussion on Tucker's forbidden substructures for matrices with
  \COP) is of prime importance.

@@

\temptext{
COP in Graph Isomorphism  -- The survey from kklv10 conclusion.
}
